
%% Author: Peter Audier
%% This is Peter Audier's .tex file for his career day resume and can be used
%  as a template.



\documentclass[10pt,letter,roman]{moderncv}
% note: other options include different font sizes (10pt, 11pt and 12pt), paper sizes (a4paper, letterpaper, a5paper, legalpaper, executivepaper and landscape) and font families (sans and roman)

% modern themes
% note: style options include casual, classic, oldstyle and banking
\moderncvstyle{banking}

% note: color options include orange, black, blue, purple, red, grey and green
\moderncvcolor{orange}

% character encoding
\usepackage[utf8]{inputenc}

% Is used for listing tools used during projects
\usepackage{multicol}

% gets rid of all page numbers
\usepackage{nopageno}

% adjust the page margins
\usepackage[scale=0.85]{geometry}


% personal data
\name{\textsc{Peter}}{\textsc{Audier}}

\phone[mobile]{978-837-2713}

\email{pxa4084@rit.edu}

\homepage{github.com/PeterAudier}

\extrainfo{\homepagesymbol\httplink{linkedin.com/in/peter-audier}}


% =====    Resume Contents    ===============================================================
\begin{document}

\makecvtitle

\normalText{A third-year student studying software engineering at Rochester Institute of Technology. Previously worked with a local town government as a project lead for a small team focused on developing a web portal for use by electrical technicians. Available starting winter of 2018.}

\section{\textsc{Job Experience}}
\begin{itemize}
    \item{\cventry{September 2018--today}{Assistant Manager}{Spirit Halloween}{Rochester,NY}{}{\vspace{3pt}Supervises and coaches Associates. Also ensures all store functions run smoothly when store manager is absent. Enforces all company policies and procedures including closing the store.}}
    \vspace{3pt}
    \item{\cventry{June 2018--August 2018}{Assistant Instructor}{Circuit Lab}{Somerville,MA}{}{\vspace{3pt} Worked with children ages 6-12 teaching programming and circuit skills. Kept open and professional communication with parents to provide the best experience for their children.}}
    \vspace{3pt}
    \item{\cventry{May 2016--August 2016}{Energy Intern}{Energize Andover}{Andover, MA}{}{\vspace{3pt} I led and instructed a team of four high school students to design and build a website for the town of Andover's Parks and Rec department.}}
    \vspace{3pt}
    \item{\cventry{May 2016--January 2017}{Data Entry Clerk}{MT Unirepair}{Wilmington,MA}{}{\vspace{3pt}Instructed other clerks on how to access and use the HP databases. Also worked in the printer repair shop helping to refurbish printers.}}
\end{itemize}

\section{\textsc{Projects}}
\begin{itemize}
\item{\normaltext{\textbf{Energize Andover}}}
\begin{itemize}
    \item A web portal used by electricians and technicians to view the circuit topology of town buildings.
    \item Tools used for the project include:
    \begin{itemize}
    \begin{multicols}{3}
      \item Django
      \item Python
      \item GitHub
      \item HTML
      \item JavaScript
      \item PostgreSQL
      \item UML
      \item CSS
      \item BACpypes
    \end{multicols}
    \end{itemize}
  \end{itemize}
  
\vspace{3pt}
\item{\normaltext{\textbf{HealthNet}}}
	\begin{itemize}
        \item A web portal designed for hospitals to connect doctors and patients.
		\item Tools gained over the course of the project include:
		\begin{itemize}
    	\begin{multicols}{3}
            \item Django
      		\item Python
     		\item Bootstrap
     		\item SQLite
     		\item SVN
     		\item JavaScript
     		\item UML
            \item CSS
        \end{multicols}
        \end{itemize}
  	\end{itemize}


\end{itemize}

\section{\textsc{Education}}


\begin{itemize}
\item{\cventry{2016--2021}{BS}{Rochester Institute of Technology}{Rochester}{\textit{Software Engineering}}{}}
\end{itemize}


\section{\textsc{Skills and Interests}}


\begin{itemize}

\item \textbf{Programming Languages:} C, C\#, Python, Django, Java, SQL, JavaScript, HTML, LaTeX, Arduino, Basic, Ruby, C++, CSS.
\vspace{5pt}
\item \textbf{Leadership Experience:} President of Venture Crew 921 for two terms, member of North Reading Union Congregational Church Council for two terms, Treasurer for Beekeeping club at RIT for one term.
\vspace{5pt}
\item \textbf{Community Service:} Member of North Reading Union Congregational Church Environmental Stewardship Ministry for four years

\end{itemize}

\end{document}